---
name: Nathan
surname: Quan
position: "Fulbright U.S. Student Finalist"
# address: "`r keyring::key_get(service = 'my_address', username = 'nathansquan')`"
# phone: "`r keyring::key_get(service = 'my_cell', username = 'nathansquan')`"
email: "`r keyring::key_get(service = 'my_email', username = 'nathansquan')`"
docname: Curriculum Vitae
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
bibliography_published: "nsnquanpubs.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(RefManageR)
# Read any bib files
pubs <- bibliography_entries("nsnquanpubs.bib")
```



# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Why,
  "MPH Epidemiology", "2020", "Emory University, Rollins School of Public Health", "Atlanta, GA", "Certificate: Socio-contextual Determinants of Health",
  "MPH Epidemiology", "2020", "Emory University, Rollins School of Public Health", "Atlanta, GA", "Thesis: Revealing the Variations in Impact of Economic Segregation on Preterm Birth Among Disaggregated Asian Ethnicities across MSAs in the United States: 2015-2017",
  "B.S. Biochemistry", "2018", "Virginia Tech", "Blacksburg, VA", "Minor: Chemistry"
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Why)
```


# Professional Experience

```{r}
tribble(
  ~ Title, ~ When, ~ Institution, ~ Where,
  "COVID-19 Case Investigator", "Aug 2020-Feb 2021", "Virginia Department of Health, Prince William Health District", "Manassas, VA",
  
  "Emory REAL Graduate Research Assistant", "Oct 2019-May 2020", "CDC Division of Global HIV and TB", "Atlanta, GA",
  
  "Pathways to Practice Scholar", "May 2019-Aug 2019", "Louisville Metro Dept. of Public Health", "Louisville, KY",
  
  "Graduate Research Assistant", "Sept 2018-May 2019", "Emory University School of Medicine", "Atlanta, GA"
) %>%
  detailed_entries(Title, When, Institution, Where)
```


<!-- # Publications -->

```{r}
# library(dplyr)
# scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>%
#   filter(cites > 30) %>%
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>%
#   RefManageR::as.BibEntry() %>%
#   RefManageR::WriteBib("curie.bib")
# 
# bibliography_entries("curie.bib")
```



# Skills

```{r Skills}
tribble(
  ~Type, ~What,
  "Programming Languages", "R, SAS",
  
  "Statistics", "linear regression, logistic regression, Poisson regression, survival analysis, inverse probability of treatment weighting analysis, mediation analysis, difference in differences, multilevel modeling",
  
  "Software", "ArcGIS , NVIVO, Microsoft Office",
  
  # "Languages", "Vietnamese (Speaking, Reading, and Writing: Beginner) and Khmer (Speaking: Beginner)"
) %>%
  detailed_entries(glue::glue("\\textbf{<Type>}: <What>", .open = "<", .close = ">"), .protect = FALSE)
```


# Publications

```{r Publications}
pubs
```

# Presentations

```{r talks}
tribble(
  ~ when, ~ title, ~ details, ~ where,
  "2019", "Applying Societal Health", "A Case Study at the Louisville Metro Department of Public Health and Wellness Against the Backdrop of a Pension Crisis", "Virginia Tech, Dept. of Science and Technology Studies",
) %>% 
  brief_entries(glue::glue("\\textbf{<title>}: <details>", .open = "<", .close = ">"), when, where, .protect = FALSE)
```

# Awards

```{r}
tribble(
  ~ award, ~ from, ~ year,
  "Fulbright U.S. Student Finalist", "Cambodia", "2020",
) %>%
  brief_entries(award, year, from)
```

# Relevant Skills
\begin{cvskills}
  \cvskill
    {Braille}
    {UEB (Unified English Braille), Nemeth (Math), Korean, Japanese Brailles}

  \cvskill
    {Data Science}
    {R (highly advanced: published 3 packages in CRAN), Python (advanced: tensorflow/keras/scikit-learn), SQL}

  \cvskill
    {Reproducible Report}
    {Markdown/Rmarkdown, R shiny apps, Jupyter Notebook, LaTeX, Pandoc, lua}

  \cvskill
    {DevOps}
    {Git, Docker, AWS, Travis CI, Cygwin}

  \cvskill
    {Front-End}
    {HTML/CSS/JS/PHP/ARIA (advanced level to design according to WCAG 2.0/2.1), WordPress, Drupal, Hugo}

  \cvskill
    {Back-End}
    {Unix/Linux Shell scripts, LAMP, Django, REST API}

  \cvskill
    {Compile Programming Languages}
    {C/C++/C\#, Java, Quorum}

  \cvskill
    {Quantitative Research}
    {t-test, within-/between-subjects/Repeated Measures ANOVAs/ANCOVAs/MANOVAs/MANCOVAs, Regressions, \newline HLM, Factor Analysis, Network Analysis, SEM, PCA, Unsupervised/Supervised Machine Learning}

  \cvskill
    {Qualitative Research}
    {Virtual Ethnography, Content Analysis, Grounded Theory, Phenomenology, Case Studies, Interaction Analysis}

  \cvskill
    {Mixed Research}
    {Text Mining, Quantitative Ethnography, Explanatory/Exploratory Sequential Mixed Methods}

  \cvskill
    {Languages}
    {English/Korean (bilingual)}
\end{cvskills}


# Peer-reviewed Publications

<!-- Notes: copy and paste the following block for any other bibliography sections with the same bibliography key matched that you assigned in YAML  -->
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#bibliography_published}
:::

\endgroup
<!-- Bib-printing block ends here. -->